Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-09-08 papers/paper_review/response_1.txt

Sincerely,

Luke Bouma

******************************************
Reviewer #1 MODERATE CONCERNS

REVIEWER COMMENT
----------
Figure 1:
- It is interesting to note that all four planets are concentrated in X-Z, vb-vl*, and vl*-l. This could be because of the small fraction of space that the Kepler field surveyed. Is that accurate? Is there any way to indicated which stars were observed by Kepler in these figures?
- Note that in B&W only the + symbol has a different color than the rest, although since the symbols are different this wasn't much of an issue. The exception is that I can't tell which group is magenta and which lime green, so specifying which are the larger filled circles and which are the smaller would be helpful.
- Why is it important to show the projection of the solar velocity?
RESPONSE
----------
> - The Kepler field is shown with the large gray squares in the top panel of the figure, between l of 70 to 85, and b of 5 to 20.  This approximately corresponds to a cone in XYZ -- in case it helps intuition, (l,b)=(90,0) corresponds to the line of X=Z=0.  The resulting concentration of the planets in v_l* follows from the narrow range of galactic longitudes that Kepler looked at, and the narrow spread in v_l* at a given galactic longitude.
>
> - We now specify in the caption which are the larger and smaller filled circles.
>
> - We have briefly summarized in the first paragraph of section 2.2 why we have shown the projection of the solar velocity: it is because we are interested in how much of the spread in v_l* it might explain.  The short answer is "some of it, but not all of it".  To give a more complete explanation: the Sun moves at ~17 km/s toward (l,b)=(53deg,23deg), relative to a hypothetical circular orbit around the center of the galaxy.  This means that in our observed frame, nearby stars on average appear to move opposite this direction.  At l=53 and 53+180 degrees, the effect does not influence v_l*.  At l=53+90 degrees, the effect on v_l* is maximized, with amplitude = v_LSR = 17 km/s.  The minimum is at l=53+270 degrees.  Figure 11 of Zari, Brown et al 2018 provides an example for how much of the variance in observed v_l* can be ascribed to this projection effect for stars near the galactic plane.  The lower-right panel of our Figure 1 however shows that while the LSR projection accounts for some of the change in observed v_l* in Cep-Her, the data and the gray band do not match!  There therefore needs to be some intrinsic differences in the UVW velocities of these stars (though v_r, v_phi, and v_z may perhaps the better coordinate system).

@@

REVIEWER COMMENT
----------
*Line 162: vb and vl* not defined
RESPONSE
----------
> Thank you for this catch -- $v_b$ is the distance-corrected proper motion in the direction of increasing galactic latitude, and $v_{l^*}=v_l \cos b$ is the same in the direction of increasing galactic longitude after accounting for the local tangent plane correction.  We have added verbiage to this effect.

REVIEWER COMMENT
----------
*Line 171: core distance metric is not defined, but is quite important per the subsequent paragraph and so should be explained. It would also be helpful to state that larger values of D are better.
RESPONSE
----------
> We have added the following clarifying sentence to the manuscript:
> \added{Core distance is the distance to the $k^{\rm th}$ nearest star, and therefore $k$ acts as a smoothing parameter, where a larger value reduces the influence of local overdensities smaller than the scale that interests us.}

REVIEWER COMMENT
----------
Line 174-175, "at least as close to the 10th nearest": Not clear what this means.
RESPONSE
----------
> The relevant sentence has been reworded for clarity.

REVIEWER COMMENT
----------
Line 188: I understand the notation for a normal distribution, but perhaps worth just writing in words instead. I also don't know why D is Gaussian in the first place, but this would presumably be explained by defining the core distance.
RESPONSE
----------
> Thank you for this catch -- the wording in the original text had a subtle error. The revised wording is as follows.
>
> "To enable a selection cut that filters out field-star contaminants, we also compute a weight metric, $D$, defined such that the group member with the smallest core distance has $D=1$, the group member with the greatest core distance has $D=0$, and the metric $D$ scales linearly between the two extremes.  After applying a set of quality cuts on the astrometry and photometry [...] this procedure yields a distribution of weights $D$ that is well described by a log-normal distribution with \log_{10}\mathcal{N}(-1.55,0.61)$."
>
> The original wording incorrectly stated that the "weights for the other group members are log-normally distributed" between the two extremes, while instead the scaling is linear.  The fact that the resulting distribution of weights is well-fit by a log-normal is an emergent property of the HDBScan clustering and our definition of D -- the attached hist_weight.png substantiates the claim that the distribution is "well-described" by such a functional form.

@@

******************************************

Other minor changes made to the manuscript include:

* The radius of Kepler-1643b was previously stated in the abstract to be 2.32 +/- 0.14 R_earth.  This was a typo, it is +/- 0.13 R_earth.

* We added the following text as a note to table 2: "\added{Users who wish to minimize field star contamination should apply more restrictive weight cuts, {\it e.g.}, $\texttt{weight}>0.1$.}"

* We reduced the axis width on all figures for visual clarity.

### 2022-09-08 papers/paper/ms.tex
update response

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{2022 May 2}
\revised{2022 Sep 6}
\accepted{---}
%\submitjournal{AAS Journals}
\shorttitle{Trio of Mini-Neptunes in Cep-Her}

@@

The unsupervised clustering in this case yielded 8 distinct subgroups.
These groups are then used as the ``seed'' populations\replaced{ for
the third step, which is to search for objects at least as close to
the 10$^{\rm th}$ nearest HDBSCAN-identified member in space-velocity
coordinates}{, in which the stellar members each have their own
individually-assigned distances to their tenth-nearest
photometrically-young neighbor.  Using those distances, we search the
entire Gaia EDR3 point source catalog for stars that fall within each
star's 10$^\th$ nearest-neighbor distance}.  This third step yields
stars that are spatially and kinematically close to the
photometrically young stars, but which cannot be identified as young
based on their positions in the color--absolute magnitude diagram.

The outcome of the analysis up to the point of the third step is shown
in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that filters
out field-star contaminants, we also compute a weight metric,
$D$, defined such that the group member with the smallest core
distance has $D=1$, the group member with the greatest core
distance has $D=0$, and \replaced{weights for the other group members are
log-normally distributed between these two extremes}{the weight $D$
scales linearly between the two extremes}.  After applying a
set of quality cuts on the astrometry and
photometry\footnote{$\varpi/\sigma_\varpi>5$; $G/\sigma_{G}>50$;
$G_{\rm RP}/\sigma_{G_{RP}}>20$; $G_{\rm BP}/\sigma_{G_{BP}}>20$}
this procedure yields \replaced{$D \sim
\log_{10}\mathcal{N}(-1.55,0.61)$}{a distribution of weights $D$
that is well described by a log-normal distribution with
\log_{10}\mathcal{N}(-1.55,0.61)$}.
To visualize the results, in Figure~\ref{fig:XYZvtang} we show
12{,}436 objects with $D>0.02$ as gray points, and 
4{,}763 objects with $D>0.10$ as black points.  \added{These thresholds were
selected visually based on the apparent purity with which they yielded
pre-main-sequence stars on a color--absolute magnitude diagram.} The
$\delta$~Lyr\ cluster is visible at $(l,b)=(68^\circ,15^\circ$) and $(v_{l^*},
v_b)=(-4.5 ,-4 )\mkms$.  RSG-5 is visible at $(l,b)=(83^\circ,6^\circ)$,
$(v_{l^*}, v_b)=(5.5 ,-3.5 )\mkms$.  Most of the other subclusters, including
in Cep-Cyg ($l,b=90^\circ,7^\circ$) and Cerberus ($l,b=48^\circ,18^\circ$) are
too small or dispersed to have previously been analyzed in great detail.

>>>>

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{2022 May 2}
\revised{2022 Sep 6}
\accepted{---}
%\submitjournal{AAS Journals}
\shorttitle{Kepler and the Behemoth}

@@

The unsupervised clustering in this case yielded 8 distinct subgroups.
These groups are then used as the ``seed'' populations\replaced{ for
the third step, which is to search for objects at least as close to
the 10$^{\rm th}$ nearest HDBSCAN-identified member in space-velocity
coordinates}{, in which the stellar members each have their own
individually-assigned distances to their tenth-nearest
photometrically-young neighbor.  Using those distances, we search the
entire Gaia EDR3 point source catalog for stars that fall within each
star's 10$^{\rm th}$ nearest-neighbor distance}.  This third step yields
stars that are spatially and kinematically close to the
photometrically young stars, but which cannot be identified as young
based on their positions in the color--absolute magnitude diagram.

The outcome of the analysis up to the point of the third step is shown
in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that filters
out field-star contaminants, we also compute a weight metric,
$D$, defined such that the group member with the smallest core
distance has $D=1$, the group member with the greatest core
distance has $D=0$, and \replaced{weights for the other group members are
log-normally distributed between these two extremes}{the weight $D$
scales linearly between the two extremes}.  After applying a
set of quality cuts on the astrometry and
photometry\footnote{$\varpi/\sigma_\varpi>5$; $G/\sigma_{G}>50$;
$G_{\rm RP}/\sigma_{G_{RP}}>20$; $G_{\rm BP}/\sigma_{G_{BP}}>20$}
this procedure yields \replaced{$D \sim \log_{10}\mathcal{N}(-1.55,0.61)$}{a distribution of weights $D$
that is well described by a log-normal distribution with
$\log_{10}\mathcal{N}(-1.55,0.61)$}.
To visualize the results, in Figure~\ref{fig:XYZvtang} we show
12{,}436 objects with $D>0.02$ as gray points, and 
4{,}763 objects with $D>0.10$ as black points.  \added{These thresholds were
selected visually based on the apparent purity with which they yielded
pre-main-sequence stars on a color--absolute magnitude diagram.} The
$\delta$~Lyr\ cluster is visible at $(l,b)=(68^\circ,15^\circ$) and $(v_{l^*},
v_b)=(-4.5 ,-4 )\mkms$.  RSG-5 is visible at $(l,b)=(83^\circ,6^\circ)$,
$(v_{l^*}, v_b)=(5.5 ,-3.5 )\mkms$.  Most of the other subclusters, including
in Cep-Cyg ($l,b=90^\circ,7^\circ$) and Cerberus ($l,b=48^\circ,18^\circ$) are
too small or dispersed to have previously been analyzed in great detail.
